\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-12 Hierarchical-forecast-reconciliation/Appendix.tex
Adjusted the table in Appendix

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}

\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\def\var{\text{Var}}

\def\PQ{\begin{pmatrix}\bm{G}\\[-0.2cm]\bm{H}\end{pmatrix}}
\def\bt{\begin{pmatrix}\tilde{\bm{b}}\\[-0.2cm]\tilde{\bm{a}}\end{pmatrix}}

%\theoremstyle{theo}
\newtheorem{theo}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{property}
\newtheorem{property}{Property}[section]

\begin{document}

	%\bibliographystyle{natbib}

	\def\spacingset#1{\renewcommand{\baselinestretch}%
		{#1}\small\normalsize} \spacingset{1}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\if1\blind
	{
		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
		\author{Puwasala Gamakumara\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			Anastasios Panagiotelis\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: george.athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

	\if0\blind
	{
		\bigskip
		\bigskip
		\bigskip
		\begin{center}
			{\LARGE\bf Hierarchical Forecasts Reconciliation}
		\end{center}
		\medskip
	} \fi

	\bigskip

	\begin{abstract} TBC
		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints. We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically. New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense. Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints. Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
	\end{abstract}

%	\noindent%
%	{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
%	\vfill

	\newpage
	\spacingset{1.45} % DON'T change the spacing!

	\section{Introduction}\label{sec:intro}

	A collection of multiple time series with some aggregation structure arises in many disciplines such as manufacturing, engineering, marketing, medicine, etc. These are often known as hierarchical time series. Making coherent forecasts for these series that are in line with the inherent aggregation constraints is an essential requirement for decision making. Early studies on this literature use a single level forecasting approaches. That is, forecasting the series in a single level of the hierarchy and then aggregate or disaggregate these forecasts to get coherent forecasts for remaining series. The well known Bottom-up \citep{Dunn1976} and Top-down \citep{Gross1990, Athanasopoulos2009} methods are examples for these traditional methods. Multiple studies also discuss the relative advantages and disadvantages of these methods, for example, \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	A shortcoming of these traditional methods is that they do not use all the information available in the hierarchy to make coherent forecasts. To overcome this issue, \cite{Hyndman2011} propose to utilise all the information available in the hierarchy via a ``Reconciliation" process. This is a two-stages process where the first stage involves making forecasts for all series in the hierarchy without considering the aggregation constraints (also known as base forecasts), which is then followed by the reconciliation stage that combines these forecasts imposing the aggregation constraints of the hierarchy. A later study by \cite{WicEtAl2019} proposed to optimally combine the base forecasts by minimising the trace of the mean squared errors of reconciled forecasts where they derived an analytical solution to produce reconciled forecasts. An important feature of this method is that it imposes the correlation structure of the whole hierarchy to produce reconciled point forecasts.

	While reviewing the existing studies in this literature, our attempt is to give a new understanding to the whole hierarchical forecasting problem with a geometric intuition. We first provide a geometric interpretation of coherency and reconciliation in terms of projections. Then we rehash all existing reconciliation methods into a single framework based on projections. In addition to being highly intuitive, this allows us to establish new theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections while the second shows that reconciliation via projections preserves the unbiasedness of base forecasts.

	Unbiasedness of base forecasts is a strong assumption in many of the existing methods which will be limited only to a selective number of forecasting methods. We propose a simple solution to this barrier. That is to correct the bias in base forecasts before doing the projection-based reconciliation. This allows using any advanced statistical method despite the unbiasedness to produce base forecasts without worrying about the unbiasedness. Using an empirical study, we further show that the reconciled forecasts follow from biased corrected base forecasts will improve the forecast accuracy compared to that of the biased forecasts.

	The remainder of this paper is structured as follows. In Section~\ref{sec:CoheForecasts} coherent point forecasting is defined geometrically while section~\ref{sec:Reconciliation} contains definitions of projection-based reconciliation as well as our main theoretical results. Section~\ref{sec:BiasInRecon} discuss the unbiased preserving property of projection-based reconciliation and Section \ref{sec:BiasCorrection} contains our proposed method to correct the bias in base forecasts. In Section \ref{sec:EmpStudy} we apply these methods to get coherent forecasts for domestic tourism flow in Australia and Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.  
\section{Coherent forecasts}\label{sec:CoheForecasts}

	\subsection{Notation and preliminaries}\label{sec:notation}

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{WicEtAl2019}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

    \begin{equation}
    \bm{y}_t = \bm{Sb}_t,
    \end{equation}
    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.

		\begin{figure}[H]
			\begin{center}
				\leaf{AA} \leaf{AB}
				\branch{2}{A}
				\leaf{BA} \leaf{BB}
				\branch{2}{B}
				\branch{2}{Tot}
				\qobitree
			\end{center}
			\caption{An example of a two level hierarchical structure.}\label{fig:basichier}
		\end{figure}

	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig:basichier}.  For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
	\[
	\bm{S} = \begin{pmatrix}
	1 & 1 & 1 & 1  \\
	1 & 1 & 0 & 0 \\
	0 & 0 & 1 & 1 \\
	& \multicolumn{2}{c}{\bm{I}_4} &
	\end{pmatrix},
	\]
	where $\bm{I}_4$ is the $4\times 4$ identity matrix.

	While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.  In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.

	\subsection{Coherence}\label{sec:cohpointf}

	The property that data adhere to some linear constraints is referred to as {\em coherence}.  We now provide definitions aimed at providing geometric intuition of hierarchical time series.

	 \begin{definition}[Coherent subspace]\label{def:cohspace}
	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
	 \end{definition}

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray colour two dimensional plane reflects the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$. The points in $\mathfrak{s}$ represents realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

	 \begin{definition}[Hierarchical Time Series]\label{def:cohspace}
	 	A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$  lie in the coherent subspace, i.e. $\bm{y}_t\in\mathfrak{s}\quad\forall t$.
	 \end{definition}

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

%	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$. Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
%	
%	\begin{figure}[H]
%		\begin{center}
%			\begin{tikzpicture}[
%			>=stealth,
%			bullet/.style={
%				fill=black,
%				circle,
%				minimum width=1.5cm,
%				inner sep=0pt
%			},
%			projection/.style={
%				->,
%				thick,
%				label,
%				shorten <=2pt,
%				shorten >=2pt
%			},
%			every fit/.style={
%				ellipse,
%				draw,
%				inner sep=0pt
%			}
%			]
%			\node at (2,3) {$s$};
%			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
%			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
%			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
%			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
%			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
%			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
%			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
%			\end{tikzpicture}
%		\end{center}
%		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
%	\end{figure}

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$. Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
	\end{definition}

    Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.  Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage. Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.  As such incoherent forecasts were not a problem in these earlier papers.

    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.  This approach does have several advantages over only forecasting a single level.  First, there is no loss of information since all bottom levels are modelled.  Second, modelling top level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.  Unfortunately, however, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.  This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.  Instead, the solution to incoherent forecasts is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}

\section{Forecast reconciliation}\label{sec:Reconciliation}

	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.  We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$, where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.  In the sequel, this subscript will be dropped at times for ease of exposition.  In the most general terms, reconciliation can be defined as follows

	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
	\end{definition}

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix has the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection. This is a fundamental property of projections and also proved in lemma 2.4 in \citet{rao1974}. In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.  We refrain from any discussion of regression models focusing instead on geometric interpretations.  However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.

	\subsection{Orthogonal projection}

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal for over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.

	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.  The discussion in that paper focuses on the case of MinT. Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.

	Consider the Euclidean distance between a forecast and the target. This is equivalent to the root of the sum of squared errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h},\tilde{\bm{y}}_{t+h}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}

		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2\ge 0$ this implies,
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}
		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h}$.  Taking the square root of both sides proves the desired result.
	\end{proof}

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}

	\end{figure}

	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  Crucially, the result is not a result that requires taking expectations.  This distance reducing property will hold for any realisation and any forecast and not just on average.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

	\subsection{Oblique Projections}\label{sec:oblique}

	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.  A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.  For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.  Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.  An even more sophisticated understanding may take the correlation between series into account.  All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.  Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.  However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

	\begin{align}
	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
	\end{align}

	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.  This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised as follows:

	\begin{theo}[General distance reducing property]\label{th:gdistred}
        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|_{\bm{W}}$ be the $L_2$ norm (in the generalised Euclidean sense with respect to $\bm{W}$) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}.
		\end{equation}
	\end{theo}
	\begin{proof}
    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
    \end{proof}

	The implication of Theorem~\ref{th:gdistred} is that if the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.

>>>>

	
	\begin{table} 
		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
		\centering\tabcolsep=0.08cm
		\tiny
		\resizebox{\linewidth}{!}{
			\begin{tabular}{lllllllllll}
				\toprule
				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
				\cmidrule(lr){1-3}
				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
				\cmidrule(lr){1-3}
				2 & A & NSW 				&  & 50  & BAA & Melbourne && 101 & FBB & Launceston, Tamar \& North\\
				3 & B & Victoria 			&  & 51  & BAB & Peninsula && 102 & FCA & North West\\
				4 & C & Queensland 			&  & 52  & BAC & Geelong && 103 & FCB& Wilderness West\\
				5 & D & South Australia     &  & 53  & BBA & Western && 104 & GAA& Darwin\\
				6 & E & Western Australia   &  & 54  & BCA & Lakes && 105 & GAB& Kakadu Arnhem\\
				7 & F & Tasmania   			&  & 55  & BCB & Grippsland && 106 & GAC& Katherine Daly\\
				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
				\cmidrule(lr){1-3} 
				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
				\cmidrule(lr){1-3}
				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\ 
				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\ 
				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\

				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
				\cmidrule(lr){1-3}
				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
				\cmidrule(lr){1-3}
				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
				\bottomrule
			\end{tabular}
		}
\end{table}
